Does the leaf economic spectrum hold within plant functional types? A Bayesian hierarchical meta-analysis

### 2018-02-16 manuscript/02_methods.Rmd
Consistent use of across-PFT (not among-PFT)
Per recommendation of Kramer.

The most complex model was the ‘hierarchical’ model, in which observed trait values were drawn from a PFT-specific multivariate normal distribution describing within-PFT variation and whose parameters were themselves sampled from a global multivariate distribution describing the variation among PFTs.
For the observed vector of traits $\mathbf{x}_{i,p}$ for sample $i$ belonging to PFT $p$:

@@

where $\mathbf{\mu}_p$ and $\mathbf{\Sigma}_p$ are the mean vector and variance-covariance matrix describing variation within PFT $p$, and $\mathbf{\mu}_g$ and $\mathbf{\Sigma}_g$ are the mean vector and variance-covariance matrix describing among-PFT (global) variation.

@@

To assess the consistency of among- and within-PFT trait trade-offs, we looked at covariance estimates for each trait pair and, where these values were significantly different from zero ($p < 0.05$),
we calculated the eigenvalues from the pairwise variance-covariance matrix for that trait pair and plotted the corresponding dominant eigenvectors centered on the mean estimates (Fig.\ 4).
This figure provides a visual representation of relative positions of PFTs in trait space and both the direction and extent of within-PFT trait covariance, and is directly analogous to conceptual figures describing hierarchical trait variability across environmental gradients as presented in, for instance, @cornwell_community_2009 and @albert_intraspecific_2010.
Due to the small number of points used to estimate across-PFT covariance in the hierarchical model, none of the across-PFT covariances estimated in the hierarchical model were significantly different from zero ($p < 0.05$).
For this reason, we compared within-PFT covariances as estimated by the hierarchical model with the covariances estimated by fitting a multivariate model to all of the data.

>>>>

The most complex model was the ‘hierarchical’ model, in which observed trait values were drawn from a PFT-specific multivariate normal distribution describing within-PFT variation and whose parameters were themselves sampled from a global multivariate distribution describing the variation across PFTs.
For the observed vector of traits $\mathbf{x}_{i,p}$ for sample $i$ belonging to PFT $p$:

@@

where $\mathbf{\mu}_p$ and $\mathbf{\Sigma}_p$ are the mean vector and variance-covariance matrix describing variation within PFT $p$, and $\mathbf{\mu}_g$ and $\mathbf{\Sigma}_g$ are the mean vector and variance-covariance matrix describing across-PFT (global) variation.

@@

To assess the consistency of within- and across-PFT trait trade-offs, we looked at covariance estimates for each trait pair and, where these values were significantly different from zero ($p < 0.05$),
we calculated the eigenvalues from the pairwise variance-covariance matrix for that trait pair and plotted the corresponding dominant eigenvectors centered on the mean estimates (Fig.\ 4).
This figure provides a visual representation of relative positions of PFTs in trait space and both the direction and extent of within-PFT trait covariance, and is directly analogous to conceptual figures describing hierarchical trait variability across environmental gradients as presented in, for instance, @cornwell_community_2009 and @albert_intraspecific_2010.
Due to the small number of points used to estimate across-PFT covariance in the hierarchical model, none of the across-PFT covariances estimated in the hierarchical model were significantly different from zero ($p < 0.05$).
For this reason, we compared within-PFT covariances as estimated by the hierarchical model with the covariances estimated by fitting a multivariate model to all of the data.
